Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-08-13 neurips-20/response/neurips_2020_author_response.tex
neurips response light pass. bo@boulder

\item 
  While straightforward, we felt it important to emphasize Theorem 1 as it is not stated clearly in the literature, and indirect elicitation is not a well known tool to reason about consistency.

@@

\item 
Infinite infimum expected loss: In this paper we assume there always exists a minimizer of expected loss. For losses, this follows by definition of $\mathcal{L}$. For properties, it follows from nonemptiness. Understanding other cases is indeed interesting; we will emphasize this assumption throughout.

>>>>

\item 
  We agree Theorem 1's proof is straightforward. We felt it important to emphasize as it is not stated clearly in the literature, and indirect elicitation is not yet a well known tool to reason about consistency.

@@

\item 
Infinite infimum expected loss: In this paper we assume there always exists a minimizer of expected loss. For losses, this follows by definition of $\mathcal{L}$. For properties, it follows from nonemptiness. Understanding other cases is indeed interesting. We will emphasize this assumption throughout.
